Hector Permafrost

### 2019-05-30 analysis/paper/paper.Rmd
Add more notes and refs to paper
Render manuscript (and fix some LaTeX issues)

Several studies have attempted to evaluate the potential economic impacts of current and future permafrost C emissions.
@lawrence_2012_simulation project declines in near-surface permafrost by 33% and 72% in RCP 2.6 and 8.5, respectively, and permafrost C feedback will stabilize at 2100 in RCP 2.6.
More recently, @hope_2015_economic projected permafrost C emissions using the SiBCASA (TODO: write in full) land surface model and used these projections as inputs to the PAGE09 integrated assessment model (IAM).
They found that XXX.
Similarly, @gonzalez-eguino_2016_significant used the DICE (TODO: write in full) model to XXX.

@@

Case 2 uses the same formulation, but splits permafrost C into its own "biome", with its own photosynthesis ($\Beta$) and respiration ($Q_{10}$) parameters.

@@

$$ \log(L) = \sum_s Normal(Hector(\Beta, Q_{10}, s) | CMIP5(s), \sigma) $$

where $s$ is one of the four representative carbon pathways (RCPs), $CMIP5(s)$ are the CMIP5 global mean outputs for the corresponding variables, and $\sigma$ is the model error (estimated during the fit).
We also used the resulting distributions for $\Beta$ and $Q_{10}$ for the non-permafrost biome in cases 2 and 3.
We feel this is appropriate because the CMIP5 models against which these parameters are calibrated do not include permafrost C feedbacks.

For case 2, we calibrated the permafrost-specific $\Beta$ and $Q_{10}$ against various literature sources, including:

@@

$$ FCRt = FCRt0 * exp(-ΔT / Γ) (for ΔT > 0.2 °C) $$

@@

@@

**Figure**: Parameter distributions from calibration.

@@

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
my_data <- readr::read_csv("../data/raw_data/my_csv_file.csv")
```

>>>>

Several studies have attempted to evaluate the potential economic impacts of current and future permafrost C emissions.
@lawrence_2012_simulation project declines in near-surface permafrost by 33% and 72% in RCP 2.6 and 8.5, respectively, and permafrost C feedback will stabilize at 2100 in RCP 2.6.
More recently, @hope_2015_economic projected permafrost C emissions using the SiBCASA (TODO: write in full) land surface model and used these projections as inputs to the PAGE09 integrated assessment model (IAM).
They found that XXX.
@chen_2019_economic also used PAGE09.
Similarly, @gonzalez-eguino_2016_significant used the DICE (TODO: write in full) model to XXX.
@kessler_2017_estimating also used DICE.

@@

Case 2 uses the same formulation, but splits permafrost C into its own "biome", with its own photosynthesis ($\beta$) and respiration ($Q_{10}$) parameters.

@@

$$ \log(L) = \sum_s Normal(Hector(\beta, Q_{10}, s) | CMIP5(s), \sigma) $$

where $s$ is one of the four representative carbon pathways (RCPs), $CMIP5(s)$ are the CMIP5 global mean outputs for the corresponding variables, and $\sigma$ is the model error (estimated during the fit).
We also used the resulting distributions for $\beta$ and $Q_{10}$ for the non-permafrost biome in cases 2 and 3.
We feel this is appropriate because the CMIP5 models against which these parameters are calibrated do not include permafrost C feedbacks.

For case 2, we calibrated the permafrost-specific $\beta$ and $Q_{10}$ against various literature sources, including:

@@

$$ FCRt = FCRt0 * exp(-\Delta T / \Gamma) (for \Delta T > 0.2 °C) $$

@@

```{r fig-parameter-distribution, fig.cap = param_dist_cap}
param_dist_cap <- paste(
  "Input parameter distributions."
)
readd(draws_plot)
```

@@

@@
